\begin{thebibliography}{99}
\bibitem{ASC} G.~Alberti,~F.~Serra~Cassano: Non-occurrence of gap for one-dimentional autonomous functionals,
Proceedings of ``Calc. Var., Homogen. and Cont. Mech.'', G.~Bouchitt\'e, G.~Buttazzo, P.~Suquet, ed.: World Sci., Singapore, p.~1--17, 1994
\bibitem{Br} F.~Brock: Weighted Dirichlet-type inequalities for Steiner symmetrization,
Calc. Var. and PDEs~{\bf8}, p.~15--25, 1999
\bibitem{Kawohl} B.~Kawohl: Rearrangements and convexity of level sets in PDE,
Lecture notes in mathematics {\bf1150}. Berlin; Springer Verlag, 1985. 134~p.
\bibitem{Lan} R.~Landes: Some remarks on rearrangements and functionals with non-constant density,
Math.~Nachr.~{\bf280}, \No5--6, p.~560--570, 2007
\bibitem{DAN} С.~Банкевич, А.~Назаров: Об обобщении неравенства Пойа-Сеге для одномерных функционалов,
Доклады Академии Наук~{\bf438}, \No1, с.~11--13, 2011
\bibitem{BGH} Дж.~Буттаццо, М.~Джаквинта, С.~Гильдебрандт: Одномерные вариационные задачи. Введение,
Научная книга, Новосибирск, 2002. 246~с.
%G.~Buttazzo, M.~Giaquinta, S.~Hildebrandt: One-dimensional Variational Problems,
%Oxford Lecture Series in Mathematics and Its Applications {\bf15}, 1998. 272 p.
\bibitem{Zh1} В.~В.~Жиков: О весовых соболевских пространствах,
Матем. сб., {\bf189}, \No8, с.~27--58, 1998
\bibitem{Zh2} В.~В.~Жиков: К проблеме предельного перехода в дивергентных неравномерно эллиптических уравнениях,
Функц. анализ и его прил., {\bf35}, \No1, с.~23--39, 2001
\bibitem{LL} Э.~Либ, М.~Лосс: Анализ, Научная книга, Новосибирск, 1998. 276~с.
\bibitem{Fed} Г.~Федерер: Геометрическая теория меры, Наука, М., 1987. 760~с.
\bibitem{Gariepy} Л.~К.~Эванс, Р.~Ф.~Гариепи: Теория меры и тонкие свойства функций, Научная книга, Новосибирск, 2002. 216~с.
%\bibitem{Gariepy} L.~C.~Evans, R.~F.~Gariepy: 
\bibitem{ET} И.~Экланд, Р.~Темам: Выпуклый анализ и вариационные проблемы, Мир, М., 1979. 400~с.

\end{thebibliography}
