\begin{thebibliography}{99}
\bibitem{ASC} G.~Alberti,~F.~Serra~Cassano: Non-occurrence of gap for one-dimentional autonomous functionals,
Proceedings of ``Calc. Var., Homogen. and Cont. Mech.'', G.~Bouchitt\'e, G.~Buttazzo, P.~Suquet, ed.: World Sci., Singapore, p.~1--17, 1994
\bibitem{Br} F.~Brock: Weighted Dirichlet-type inequalities for Steiner symmetrization,
Calc. Var. and PDEs~{\bf8}, p.~15--25, 1999
\bibitem{Kawohl} B.~Kawohl: Rearrangements and convexity of level sets in PDE,
Lecture notes in mathematics {\bf1150}. Berlin; Springer Verlag, 1985. 134~pp.
\bibitem{Lan} R.~Landes: Some remarks on rearrangements and functionals with non-constant density,
Math.~Nachr.~{\bf280}, N5--6, p.~560--570, 2007
\bibitem{DAN} S.~Bankevich, A.~Nazarov: A generalization of the P\'olya-Szeg\"o inequality for one-dimensional functionals,
Doklady RAN~{\bf438}, N1, p.~11--13, 2011 (Russian).

English translation in:
Doklady Mathematics~{\bf83}, N3, p.~287--289, 2011
\bibitem{BGH} G.~Buttazzo, M.~Giaquinta, S.~Hildebrandt: One-Dimentional Variational Problems. An Introduction,
Oxford Lecture Series in Mathematics and Its Applications {\bf15},
Oxford University Press, New York, 1998. viii+262~pp.
\bibitem{Zh1} V.~Zhikov: Weighted Sobolev spaces,
Mat. Sb.~{\bf189}, N8, p.~27--58, 1998 (Russian).

English translation in:
Sb. Math.~{\bf189}, N8, p.~1139--1170, 1998
\bibitem{Zh2} V.~Zhikov: To the Problem of Passage to the Limit in Divergent Nonuniformly Elliptic Equations,
Funkts. Anal. Prilozh.~{\bf35}, N1, p.~23--39, 2001 (Russian).

English translation in:
Funct. Anal. Appl.~{\bf35}, N1, p.~19--33, 2001
\bibitem{LL} E.~Lieb, M.~Loss: Analysis, second edition,
American Mathematical Soc., 2001. 346~pp.
\bibitem{Rudin} W.~Rudin: Functional analysis,
McGraw-Hill, 1991. 424~pp.
\bibitem{Gariepy} L.~C.~Evans, R.~F.~Gariepy: Measure Theory and Fine Properties of Functions,
CRC Press, 1991. 288~pp.

\end{thebibliography}
